An Embedding Framework for Consistent Polyhedral Surrogates

### 2022-05-24 poly-embed-journal/poly-embed-journal.tex

\subsubsection{Constructuon}
To prove Theorem \ref{thm:link-main}, it now suffices to show that for any polyhedral $L$ embedding some $\ell$, there exists a \emph{separated} link $\psi$ with respect to $L$ and $\ell$.
Construction~\ref{const:eps-thick-link}, discussed next, ``thickens'' a given embedding to produce a link.
Theorem \ref{thm:thickened-separated} states that, for a small enough choice of $\epsilon$, that link is separated.

>>>>

\subsubsection{Construction}
To prove Theorem \ref{thm:link-main}, it now suffices to show that for any polyhedral $L$ embedding some $\ell$, there exists a \emph{separated} link $\psi$ with respect to $L$ and $\ell$.
Construction~\ref{const:eps-thick-link}, discussed next, ``thickens'' a given embedding to produce a link.
Theorem \ref{thm:thickened-separated} states that, for a small enough choice of $\epsilon$, that link is separated.
